Parsing Postfix log files

### 2008-08-01 doc/logparser-background.tex
Added sample output for one of the SQL examples.

If the database supports sub-selects percentages can be obtained:
\footnote{\SQL{} note: $||$ is the concatenation operator in SQLite3; if
the database containing the extracted data does not support this syntax,
then simply remove `` $||$ '$\%$'\hspace{1ex}'' from the query --- the
results will be the same, just slightly less visually pleasing.}

\begin{verbatim}
SELECT name, description, restriction_name, hits_total,
        (hits_total * 100.0 /
            (SELECT SUM(hits_total)
                FROM rules
                WHERE postfix_action = 'REJECTED'
            )
        ) || '%' AS percentage
    FROM rules
    WHERE postfix_action = 'REJECTED'
    ORDER BY hits_total DESC;
\end{verbatim}

XXX GIVE SAMPLE OUTPUT FOR THE SNIPPET ABOVE\@.

>>>>

If the database supports sub-selects percentages can be obtained for the
top ten restrictions:

\begin{verbatim}
SELECT restriction_name, hits_total,
        (hits_total * 100.0 /
            (SELECT SUM(hits_total)
                FROM rules
                WHERE postfix_action = 'REJECTED'
            )
        ) || '%' AS percentage
    FROM rules
    WHERE postfix_action = 'REJECTED'
    ORDER BY hits_total DESC
    LIMIT 10;
\end{verbatim}

\begin{table}[ht]
    \caption{Truncated sample output from SQL query showing percentages}
    \empty{}\label{Truncated sample output from SQL query showing
    percentages}
    \begin{tabular}[]{lrr}
        \tableline{}
        Restriction & Number of hits & Percentage of hits \\
        \tableline{}%
        \input{build/sample-sql-output-include.tex}
        \tableline{}
    \end{tabular}
\end{table}
